Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-04-25 PAPER.tex
Wed Apr 25 07:47:42 EDT 2018

Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data have an additive contaminant given by
\begin{equation}
\Delta_i = \sigma_i + \phi m_i
\end{equation}
where the properties of $\sigma_i$ are as before,
%\begin{eqnarray}
%\langle \sigma_i \rangle & = & 0 \\
%\langle \sigma^2_i \rangle & = & s \\
% \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
%\end{eqnarray}
but now $\phi$ is a random variable and $m_i$ is a fixed function of $i$ with
\begin{equation}
\langle \phi \rangle = 0; \;
\langle \phi^2 \rangle = f; \; 
 \langle \phi \phi^T \rangle = f m m^T \equiv F; \;
 m^T m = 1
\end{equation}
Here $m$ represents a mode which is correlated across many data points, with correlation given by $m m^T$, and, and the amplitude of its realization is $\phi$.

>>>>

Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data have an additive contaminant given by
\begin{equation}
\Delta_i = \sigma_i + \phi m_i
\end{equation}
where the properties of $\sigma_i$ are as before,
%\begin{eqnarray}
%\langle \sigma_i \rangle & = & 0 \\
%\langle \sigma^2_i \rangle & = & s \\
% \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
%\end{eqnarray}
but now $\phi$ is a random variable and $m_i$ is a fixed function of $i$ with
\begin{equation}
\langle \phi \rangle = 0; \;
\langle \phi^2 \rangle = f; \; 
 \langle \phi \phi^T \rangle = f m m^T \equiv F; \;
 m^T m = 1
\end{equation}
Here $m$ represents a mode which is correlated across many data points, with amplitude given by  $\phi$.

Here we can again calculate the estimator given by \ref{eq:} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
\begin{equation}
\xi \equiv \frac{f/s}{1+f/s}
\end{equation} 
we have
\begin{equation}
\invC %& = & \frac{1}{s} I - \frac{g}{1+g/s} \frac{1}{s^2} m m^T \\
=   \frac{1}{s} \left(I - \xi m m^T \right)
\end{equation}
and the virtue of weighting by $\invC$ becomes clearer: in the limit $f \gg s$, $\xi \to 1$, and this becomes
\begin{equation}
\invC  = \frac{1}{s} \left(I - m m^T \right)
\end{equation}
where $I - m m^T$ is the projection operator, projecting out $m$ from any any vector it acts on.   Proceeding to calculate the full estimator
\begin{equation}
\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) = \frac{ \Delta^T  (I -  (\eta^2 - 2 \eta)  m m^T)  \Delta}{N + \eta^2 - 2 \eta} 
\end{equation}
we note that the expectation is
\begin{equation}
\hat{s} = 
\end{equation}
